### 2016-08-26 ms/ms.tex
finished first full draft of manuscript, added plants to turnover analyses

\begin{abstract}
  TO BE RE-WRITTEN
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network disassembly,
  therefore, is a priority for system-level conservation biology.  We
  explore the assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. 
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The most widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that a new species
is more likely to interact with species that are already
well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some indication
assembly occurred through preferential attachment. Network nestedness,
a pattern of interactions where a generalist core interacts with both
specialist and generalist species, increased as the community aged
\citep{albrecht2010plant}. Increasing nestedness could result from
preferential attachment process where specialist species attach to the
well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or changing points, are observed in social networks
responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}.  In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the behavior of the interactors.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,]{parker1997scale}. In pollination systems, the time since
an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating effective restoration of networks is especially
imperative in areas where species interactions provide essential
ecosystem services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which are capable of providing
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure provision the continued provision
of ecosystem services and curb biodiversity loss, effective
restoration of pollinators and their interactions in agricultural
landscapes is critical.

%% hedgerows!!  
To promote pollinator services in agriculture, farmers are
increasingly turning to the habitat restoration technique of planting
strips of native plants along farm edges (hedgerows) to help provide
habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural
landscapes\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about the assembly
of the network following hedgerow restoration.

Using a long-term dataset of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species still persists. We test
whether the species are most variable in their network position ---
and thus important contributors network reorganizations --- are less
persistent and connected species. To further explore the mechanisms
underlying the temporal dynamics in the networks, we examine patterns
in the species and interaction temporal turnover. Lastly, we
investigate whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is comprosed of
intensively managed agriculture -- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca. 3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

Monitoring began in 2006 and continued through 2015. Surveys of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of sampling, the order in which sites
were sampled was randomized. Surveys were conducted under sunny
conditions when the temperature was above $21^{\circ}\mathrm{C}$ and
wind speed was below $2.5$ meters/second.

@@

Quantitative networks were generated for each site through time. To
account for the unequal number of surveys between years (Tables
S1-S3), we use the mean of the interactions between a pair of plants
and pollinators across surveys within a year to represent intearction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of communities (also called modules or compartments). Change
point detection methods have yet to be generalized to quantitative
networks, so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E \subseteq {V × V
}$. The GHRG model decomposes the $N$ vertices into a series of nested
groups, the relationships among which are represented by the
dendrogram $T$. The tips of $T$ are the vertices of $G$, and the
probability that two vertices $u$ and $v$ connect is given by the
parameter $p_r$. The probability distribution of the network $G$ thus
defined as:

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of nine years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We emploied
code published online by L.~Peel for the change point
analysis. Analyses we conducted in Python 3.4.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their role
and thus contribute more strongly to network reorganization. We test
the that more persistent species with the highest degree are the most
stable in their network position, as would be expected is the networks
were assembling via preferential attachment.

@@

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
pollinator species and interaction turnover. Assembling networks may
have higher rates of species turnover than non-assembling communities
because new species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of species and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were response variables in
a linear mixed models with site type as an explanatory variable along
with random effects for both year and site \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develope a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. The connectance
--- the proportion of observed out of possible interactions --- is
also expected to increase as species preferentially attach to the
core. The network specialization may also change as the community
assembles. If specialist species colonize the network or species begin
to limit their interaction niche breath as the network assembles,
network-level specialization will increase \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimate the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

@@

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and the number of pollinators that secondarily went extinct is
calculated. The area below the extinction curve is an estimate of
network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of vertices, or species \citep{costa2007characterization} --- the
larger the algebraic connectivity, the more robust a network is to
cascading perturbations (Gaiarsa et al., submitted), and the harder it
is to break the community into isolated groups of species.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints}).  All five of
the assembling hedgerows experienced changing points, whereas only
$40\%$ and $81\%$ of non-assembling hedgerows and field margins,
respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (estimate of the
difference in the odds ratios between assembling and non-assembling
networks, $3.316$, $95\%$ CI $[1.314, 8.572]$, $p$-value=
$0.0117$). Network assembly following restoration is thus punctuated
by more interaction reorganizations than would be expected by
environmental shifts that would effect assembling and non-assembling
networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (estimate of the slope of
closeness variability and persistence $\pm$ standard error of the
estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of closeness
variability and degree, $0.008 \pm 0.002$, $p$-value='$0.002$). In
addition, plant persistence and degree were not significantly related
to network position variability (estimate of the slope of closeness
variability and persistence $\pm$ standard error of the estimate,
$-2.063 \pm 3.091$, $p$-value=$0.5$; slope of closeness variability
and degree, $0.0018 \pm 0.002$, $p$-value=$0.3$). The variability of
species network position was not the result of closeness linearly
increasing through time, and, in fact, plant and pollinator closeness
decreased slightly through time (Fig.~S1, estimate of the slope of
closeness through time $\pm$ standard error of the estimate,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not me biologically
significant.

>>>>

\begin{abstract}
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network assembly, therefore,
  is a priority for system-level conservation biology. We explore the
  assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. Species are highly
  dynamic in their positions in the networks, such that we find that
  assembly is punctuated by significant reorganizations of
  interactions. Non-assembling mature hedgerows and weedy field
  margins did not undergo as many network reorganizations, suggesting
  environmental factors alone cannot account for the changes observed
  in assembling communities. Pollinator species were highly
  opportunistic, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turn over
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Assembling networks also increased in nestedness through
  time, though this did not make them more robust to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The most widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some evidence that
assembly occurred through preferential attachment. Network nestedness,
a pattern of interactions where a generalist core interacts with both
specialist and generalist species, increased as the community aged
\citep{albrecht2010plant}. Increasing nestedness could result from
preferential attachment process where specialist species attach to the
well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}.  In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration.

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating network restoration is especially imperative in areas
where species interactions provide essential ecosystem services, such
as crop pollination. In intensively managed agricultural landscapes,
the demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure provision the continued provision of ecosystem services and
curb biodiversity loss, effective restoration of pollinators and their
interactions in agricultural landscapes is critical.

%% hedgerows!!  
To promote pollinator services in agriculture, farmers may chose to
plant strips of native plants along farm edges (hedgerows) to help
provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

Using a long-term dataset of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is composed of intensively
managed agriculture --- primarily monocultures of conventional row
crops, vineyards and orchards. Hedgerows we planted along field
margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep{kremen-2015-602, mgonigle-2015-x}. The mean distance between
monitoring sites was 15 km, and the minimum distance between sites of
the same type sampled in the same year was 2 km.  The entire area
surveyed spanned almost 300 km$^2$. The crop fields adjacent to all
sites were similarly managed as intensive, high-input monoculture.

Monitoring began in 2006 and continued through 2014. Surveys of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of sampling, the order in which sites
were sampled was randomized. Surveys were conducted under sunny
conditions when the temperature was above $21^{\circ}\mathrm{C}$ and
wind speed was below $2.5$ meters/second.

@@

Quantitative networks were generated for each site through time. To
account for the unequal number of surveys between years (Tables
S1-S3), we use the mean of the interactions between a pair of plants
and pollinators across surveys within a year to represent interaction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of communities (also called modules or compartments). Change
point detection methods have yet to be generalized to quantitative
networks, so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative community structure
patterns at all scales in the network \citep{peel2014detecting}. A
network $G$ is composed of vertices $V$ and edges $E$. The GHRG model
decomposes the $N$ vertices into a series of nested groups, the
relationships among which are represented by the dendrogram $T$. The
tips of $T$ are the vertices of $G$, and the probability that two
vertices $u$ and $v$ connect is given by the parameter $p_r$. The
probability distribution of the network $G$ thus defined as:

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of eight years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We employed
code published online by L.~Peel for the change point
analysis. Analyses we conducted in Python 3.4.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their role
and thus contribute more strongly to network reorganization. We test
whether the more persistent species with the highest degree are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

@@

Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. Assembling networks may have higher
rates of pollinator turnover than non-assembling communities because
new pollinator species are colonizing and establishing themselves
\citep{mgonigle-2015-x}. Similarly, if pollinators try to maximize
their foraging efficiency based on the species present, interactions
may turnover more quickly than in established communities. In
addition, at assembling hedgerows, plants may ``colonize'' the
networks as they become more attractive resources.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more turnover of
species and interactions than non-assembling communities, the species
and interaction temporal turnover estimates were included as response
variables in a linear mixed models with site type as an explanatory
variable along with a random effect of site \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Modules in the network
may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like a pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid as would be expected with
preferential attachment, nestedness would increase through time. The
connectance --- the proportion of observed out of possible
interactions --- is also expected to increase as species
preferentially attach to the core. \flagged{Is this true?} Lastly, the
network specialization may change as the community assembles. If
specialist species colonize the network or species begin to limit
their interaction niche breath as the network assembles, network-level
specialization will increase \citep{bluthgen-2006-9}.

To evaluate network nestedness, we used the estimator weighted NODF
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and interaction frequency distributions
\citep{Galeano2009}. We evaluate network specialization with the
metric H2, which estimates the deviation of the observed interaction
frequency between plants and pollinators from a null expectation where
all partners interact in proportion to their abundances
\citep{bluthgen-2006-9}. It ranges from zero for generalized networks
to one for specialized networks.

@@

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss and to cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and then calculate the number of pollinators that secondarily went
extinct. The area below the extinction curve is an estimate of network
robustness \citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization}. The larger the algebraic
connectivity, the more robust a network is to cascading perturbations,
and the harder it is to break the community into isolated groups of
species (Gaiarsa et al., submitted).

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints}).  All five of
the assembling hedgerows experienced network changing points, whereas
only $40\%$ and $81\%$ of non-assembling hedgerows and field margins,
respectively, underwent significant interaction
reorganizations. Assembling hedgerows had significantly more changing
points than the non-assembling networks (estimate of the difference in
the odds ratios between assembling and non-assembling networks,
$3.316$, $95\%$ CI $[1.314, 8.572]$, $p$-value= $0.0117$). Network
assembly following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts alone
that would effect assembling and non-assembling networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (estimate of the slope of
closeness variability and persistence $\pm$ standard error of the
estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of closeness
variability and degree, $0.008 \pm 0.002$, $p$-value=$0.002$). In
addition, plant persistence and degree were not significantly related
to network position variability (estimate of the slope of closeness
variability and persistence $\pm$ standard error of the estimate,
$-2.063 \pm 3.091$, $p$-value=$0.5$; slope of closeness variability
and degree, $0.0018 \pm 0.002$, $p$-value=$0.3$). The variability of
species network position was not the result of closeness linearly
increasing through time, and, in fact, plant and pollinator closeness
decreased slightly through time (Fig.~S1, estimate of the slope of
closeness through time $\pm$ standard error of the estimate,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not me biologically
significant.

\subsection*{Species and interaction turnover}
The rates of plant, pollinator and interaction temporal turnover were
similar across assembling hedgerows, non-assembling hedgerows and
field margins, though mature hedgerows has marginally significantly
less pollinator turnover than field margins (estimate $\pm$ standard
error of the estimate of the difference in turnover between field
margins and mature hedgerows, $-0.0498 \pm 0.026$,
$p$-value=$0.058$). When interactions where weighted by their
similarity, both assembling and mature hedgerows had higher rates of
turnover than field margins (estimate $\pm$ standard error of the
estimate of the difference in turnover between field margins and
assembling hedgerows, $0.115 \pm 0.027$, $p$-value=$0.0002$; field
margins and mature hedgerows, $0.082 \pm 0.024$,
$p$-value=$0.002$). The weighted interaction turnover at assembling
hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.
